Arc Blanc: a real time ocean simulation framework

### 2025-01-20 paper.tex
Fixed the typo
Fixed another typo

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Calculate the mask}
The FDM needs the height of the vertices below the body.
This is computed from the mask, composed of the vertices of $Z$ contained into one intersection polygon at least.
This is done using the \textbf{Point in Polygon} strategy described in Haines (1994) \cite{hainesPointPolygonStrategies1994} and later in Cormen (2001) \cite{CormenIntroductionAlgorithms2001}.

@@

To reduce the computation times, this strategy is applied to the vertices $v$ included into the bounding box of the intersections polygons.
Since the number of vertices $v$ of $Z$ is at least twice as the size of $M$, this simple technic reduces efficiently the number of ray to polygon calculations.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Calculate the mask}
The FDM needs the height of the vertices below the body.
This is computed from the mask, composed of the vertices of $Z$ contained in one of the intersection polygons at least.
This is done using the \textbf{Point in Polygon} strategy described in Haines (1994) \cite{hainesPointPolygonStrategies1994} and later in Cormen (2001) \cite{CormenIntroductionAlgorithms2001}.

@@

To reduce the computation times, this strategy is applied to the vertices $v$ included into the bounding box of the intersections polygons.
Since the number of vertices $v$ of $Z$ is at least twice as the size of $M$, this simple method reduces efficiently the number of ray to polygon calculations.
